Composable Generalized Consensus

### 2015-05-15 paper/abstract3.tex
work on the abstract
Modified the abstract

The key novelty of our framework is its practical applicability, with state
of the art optimization and reconfiguration techniques being built-in:
tolerating k faults with k + 1 replicas, executing commutative commands
without synchronization, optimizing the execution of read-only commands, and
checkpointing.

To demonstrate our framework we present two abstract composable algorithms
characterizing two popular types of quorum systems. We demonstrate that concrete
algorithms can easily be obtained by refinement from the abstract algorithms, as
evidenced by TLA+ specifications ready to be checked by the TLC model checker.
}

>>>>

The key novelty of our framework is its practical applicability. 
Our framework is based on Generalized Paxos, therefore providing buit-in support
for algorithms optimizing the execution of commuting commands.
Moreover, we propose two specifications 
capturing the essence of modular SMR algorithms based on quorum systems.
We demonstrate that concrete
algorithms can easily be obtained by refinement from our abstract specifications, as
evidenced by TLA+ specifications ready to be checked by the TLC model checker.

}
